---
title: "MarkdownReport"
author: "Giovanni Ferrigato"
date: "2024-01-09"
output: html_document
---

# My first markdown document

Here you can add some text

In this case you attain a result:
```{r, eval = T}
2 + 3
```

In this case you do not:
```{r, eval = F}
2 + 3
```

Using proper packages; the imageRy package has been built at Alma Mater for 
learning remote sensing: 
```{r, eval = T}
library(imageRy)
```

The list of the data:
```{r, eval = T}
im.list()
```

Importing the Mato grosso area image (with warning):
```{r, eval = T}
mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```

Importing the Mato grosso area image (without warning):
```{r, eval = T, warning=FALSE}
mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```

In order to get info on the image, just type the name of the object:
```{r, eval = T}
mato1992 
```

Making a new plot of the Mato grosso area with NIR over the green band:  
```{r, eval = T}
im.plotRGB(mato1992, r=2, g=1, b=3)
```

Plotting several images altogether:
```{r, eval = T}
par(mfrow=c(2,2))
im.plotRGB(mato1992, r=1, g=2, b=3)
im.plotRGB(mato1992, r=2, g=1, b=3)
im.plotRGB(mato1992, r=3, g=2, b=1)
im.plotRGB(mato1992, r=1, g=3, b=2)

```

Calculating spectral indices:
```{r, eval = T}
library(terra)
library(viridis)
dvi <- mato1992[[1]] - mato1992[[2]]
viridisc <- colorRampPalette(viridis(7))(225)
plot(dvi, col=viridisc)
```
